Beliefs about the development of mental life

### 2021-10-27 supplement/supplement-main.Rmd
tweaks and typos
add alpha

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4). All studies were approved by [IRB information removed to preserve anonymity]. All materials used in these studies are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52 (DOI: 10.17605/OSF.IO/XRZND). All studies were approved by [IRB information removed to preserve anonymity].

@@

@@

@@

##### bodily sensation

>>>>

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).

All materials used in these studies are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52 (DOI: 10.17605/OSF.IO/XRZND).

All studies were approved by [IRB information removed to preserve anonymity].

@@

```{r s2 cap ratings reliability}
d2_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Bodily sensation") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d2_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Negative affect") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d2_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Social connection") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d2_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Cognition and control") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()
```

@@

```{r s3 cap ratings reliability}
d3_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Bodily sensation") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d3_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Negative affect") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d3_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Social connection") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()

d3_cap_ratings %>%
  unite(ResponseId_target, c(ResponseId, target)) %>%
  distinct(ResponseId_target, factor, capacity, response) %>%
  filter(factor == "Cognition and control") %>%
  select(-factor) %>%
  spread(capacity, response) %>%
  column_to_rownames("ResponseId_target") %>%
  psych::alpha()
```

@@

##### Bodily sensation
